---
title: "introduction"
author : "Seongmin Cheon"
date : "23, Aug, 2023"
output: rmarkdown::html_vignette
#output: md_document

vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## EnrichR2GOplot tutorial

This packages are refer other two packages, **EnrichR** and **GOplot**.\
EnrichR see <https://maayanlab.cloud/Enrichr/>\
GOplot see <https://wencke.github.io>\
This package was created to process EncirhR result data and use it for GOplot. Therefore, you must use the version of GO DB specified below. ---

**requirement packages**

devtools\
tidyverse\
GOplot\
enrichR

# Installation

```{r, eval=F}
if (!require("devtools", quietly = TRUE))
    install.packages("devtools")
if (!require("tidyverse", quietly = TRUE))
    install.packages("tidyverse")
if (!require("GOplot", quietly = TRUE))
    install.packages("GOplot")
if (!require("enrichR", quietly = TRUE))
    install.packages("enrichR")

devtools::install_github("seongminlab/EnrichR2GOplot")
```

# Usage example

```{r setup}
#library(EnrichR2GOplot)
library(GOplot)
devtools::load_all()
```

## 1.Example dataset for EncirhR to GOdb

```{r}
data(DEPs)
head(DEPs)
```

```{r}
data(GOdb)
print(GOdb)
```

```{r}
# Minimum cut-off of adj.p-value for encirhment analysis by EnrichR,  you can use 1 (not use for p-value filter) or 0.01 (strict cut-off)
cutoff <- 0.05
```

## 2. EnrichR2GOplot

```{r}
result <- EnrichR2GOplot(DEPs, GOdb,cutoff)

GO.result <- result$EnrichR.GO
KEGG.result <- result$EnrichR.KEGG
circ <- result$circ
```

## 3. Visualize circ with GOplot pkg

see other visualize options <https://wencke.github.io>

```{r , fig.width =16, fig.height = 10, dpi = 100}
GOBar(circ, display="multiple")
```

```{r , fig.width =16, fig.height = 10, dpi = 100}
GOBubble(circ, labels = 3)
```

```{r , fig.width =16, fig.height = 10, dpi = 100}
GOBubble(circ, title = 'Bubble plot with background colour', display = 'multiple', bg.col = T, labels = 3)  
```

## 4. Export GO and KEGG results by EnrichR & GOplot

```{r}
#result <- EnrichR2GOplot(DEPs, GOdb,cutoff)
export <- export_table_EnrichR2GOplot(result, DEPs, cutoff)
```

```{r, eval=F}
head(export$Export.EnrichR2GOplot.GO)
head(export$Export.EnrichR2GOplot.KEGG)
```

```{r,echo=F}
rmarkdown::paged_table(head(export$Export.EnrichR2GOplot.GO))
```

```{r,echo=F}
rmarkdown::paged_table(head(export$Export.EnrichR2GOplot.KEGG))
```

```{r, eval=F}
library(openxlsx)

output_xlsx <- createWorkbook()
sheet1 <- "GeneOntologyResults"
sheet2 <- "KEGG_Results"

addWorksheet(output_xlsx , sheet1)
addWorksheet(output_xlsx , sheet2)

writeDataTable(output_xlsx,sheet1,export$Export.EnrichR2GOplot.GO)
writeDataTable(output_xlsx,sheet2,export$Export.EnrichR2GOplot.KEGG)

saveWorkbook(output_xlsx, file = "Export_DEPs_EnrichR2GOplot_Aug_2023.xlsx")

```

------------------------------------------------------------------------

# Options

Support two functions\
1. Uniprot Accession to Gene Name\
2. Running EnrichR and export by table

## 1. Uniprot Accession to Gene Name

```{r}
Accession <- c("O95905-1","P04439-2","P08246")
Uniprot_to_GeneNames <- UniprotAccession2GeneName(Accession)
```

```{r,echo=F}
rmarkdown::paged_table(Uniprot_to_GeneNames)
```

## 2. Run EnrichR with user selected GO database

database were selected from EnrichR homepage

```{r}
library(enrichR)
setEnrichrSite("Enrichr")
dbs <- listEnrichrDbs()
head(dbs)
```

```{r, echo=F}
rmarkdown::paged_table(dbs)
```

```{r}
Select_DB <- c("GO_Molecular_Function_2015","GO_Cellular_Component_2015","GO_Cellular_Component_2015")
#or others.... 
```

```{r, eval=F}
head(Select_DB)
```

```{r, echo=F}
data(DEPs)
Genes <- data.frame(GeneName = DEPs$GeneName) 
print(Select_DB)
```

```{r, eval=F}
head(Genes)
```

```{r, echo=F}
rmarkdown::paged_table(Genes)
```

```{r, eval=F}
#Run EnrichR with selected database
DEPs2EncirhR(Genes, Select_DB)
```

```{r}
sessionInfo()
```
